---
title: "Week 12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(PPBDS.data)
library(rstanarm)
library(tidyverse)

# Same data clean up as last week.

week_12 <- shaming %>% 
  mutate(age = 2006 - birth_year) %>% 
  mutate(treatment = fct_relevel(treatment, "Control")) %>% 
  mutate(solo = ifelse(hh_size == 1, TRUE, FALSE)) %>% 
  select(-general_04, -no_of_names, -birth_year, -hh_size) 
```


## Scene 1

**Prompt:** Create a fitted model object called `fit_1` using this formula or, if you want, a formula which you prefer. You are trying to model `age` as a function of various parameters.

age ~ sex + solo + primary_02 + primary_04 + treatment + sex:solo

```{r}
fit_1 <- stan_glm(age ~ sex + solo + primary_02 + 
                    primary_04 + treatment + sex:solo,
                  data = week_12,
                  refresh = 0)
```

                    
* Is this a causal or predictive model? Why?

Predictive b/c age is the outcome, treatments don't make you older/younger

* Interpret the fitted model. 
Intercept: average age for female living w/ people who didn't vote in either primary and was not subject to a treatment (was in control).

* Should we keep all these variables? And the interaction term?

Treatment doesn't make sense because receiving certain voting treatments shouldn't be predictive of age / it's not significant in the model.

* Are you surprised about the meaningfulness, or lack thereof, for the treatment variables?

not surprised? If treatments are randomly assigned they shouldn't be correlated w/ age




## Scene 2

**Prompt:** Provide a posterior probability distribution for the expected difference in ages between those who live alone and those who do not. (Hint: Given that we are asking for an expected value, use `posterior_epred()`.)


```{r}
newobs <- expand_grid(solo = c(TRUE, FALSE), sex = c("Male", "Female"),
                 primary_02 = "No", primary_04 = "No",
                 treatment = "Control")

pe <- posterior_epred(fit_1, newdata = newobs) %>%
  as_tibble() %>%
  rename('male_t' = `1`,
         'female_t' = `2`,
         'male_f' = `3`,
         'female_f' = `4`) %>%
  mutate(male_diff = male_t - male_f,
         female_diff = female_t - female_f) %>%
  select(male_diff, female_diff) %>%
  pivot_longer(cols = male_diff:female_diff, 
               values_to = "diff", 
               names_to = "gender")

pe %>%
  ggplot(aes(x = diff, y = after_stat(count/sum(count)),
             fill = gender)) + 
    geom_histogram(color = "white", bins = 50,
                   position = "identity", alpha = 0.5) +
    scale_y_continuous(labels = scales::percent_format())
```





